Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-02-27 xrb/paper.tex
Clarify wording where we specify where in the initial model we set the temperature vs the entropy.

Creating the model involves specifying $T_\star$, $T_\mathrm{hi}$,
$T_\mathrm{lo}$, $\rho_\mathrm{int}$, $H_\star$,
$\delta_\mathrm{atm}$, ${X_k}_\star$, ${X_k}_\mathrm{atm}$, and $g$.  We
then integrate outwards from the base of the ramp region ($y =
H_\star$), enforcing the discrete form of hydrostatic equilibrium,
Eq.~\ref{eq:hse}.  Integrating upwards, we find $p_i$ and
$\rho_i$ using a Newton-Raphson solver together with the equation of state, with either the temperature
specified, $T_i = T(p_i, \rho_i, \{X_k\}_i)$ (in the isothermal, ramp,
and buffer layers) or constant entropy, $s_i = s(p_i, \rho_i,
\{X_k\}_i)$, in the fuel layer.  This follows the procedures described in \citet{ppm-hse}.  We
use a constant temperature for all $y < H_\star +
3\delta_\mathrm{atm}$.  Above this, we switch to an isentropic atmosphere until the
temperature drops to a floor value, $T_\mathrm{lo}$, at which point we
again keep the temperature constant.  The integration of the
atmosphere continues until the density falls to a low density cutoff,
$\rho_\mathrm{cutoff}$.  The material above this height is taken to
have constant density and temperature.
The choice of factors in front of $\delta_\mathrm{atm}$ were designed
to make sure the peak $T$ is attained at the desired density
of the burning layer.
The parameters we use for
the model generation are listed in Table~\ref{table:params} and the 
initial model profiles are showing in Figure~\ref{fig:initial_models}.

>>>>

Creating the model involves specifying $T_\star$, $T_\mathrm{hi}$,
$T_\mathrm{lo}$, $\rho_\mathrm{int}$, $H_\star$,
$\delta_\mathrm{atm}$, ${X_k}_\star$, ${X_k}_\mathrm{atm}$, and $g$.  We
then integrate outwards from the base of the ramp region ($y =
H_\star$), enforcing the discrete form of hydrostatic equilibrium,
Eq.~\ref{eq:hse}.  Integrating upwards, we find $p_i$ and
$\rho_i$ using a Newton-Raphson solver together with the equation of state, with either the temperature
specified, $T_i = T(p_i, \rho_i, \{X_k\}_i)$ (in the neutron star, ramp,
and isothermal buffer layers) or constant entropy, $s_i = s(p_i, \rho_i,
\{X_k\}_i)$, in the fuel layer.  This follows the procedures described in \citet{ppm-hse}.  We
use a constant temperature for all $y < H_\star +
3\delta_\mathrm{atm}$.  Above this, we switch to an isentropic atmosphere until the
temperature drops to a floor value, $T_\mathrm{lo}$, at which point we
again keep the temperature constant.  The integration of the
atmosphere continues until the density falls to a low density cutoff,
$\rho_\mathrm{cutoff}$.  The material above this height is taken to
have constant density and temperature.
The choice of factors in front of $\delta_\mathrm{atm}$ were designed
to make sure the peak $T$ is attained at the desired density
of the burning layer.
The parameters we use for
the model generation are listed in Table~\ref{table:params} and the 
initial model profiles are showing in Figure~\ref{fig:initial_models}.
